Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-11 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
Section V.D

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function on coupling constant $\ell_{\rm GB}$ in EdGB gravity
for GW150914 (top panel), GW200129 (middle panel)
and from combining results (bottom panel).
%
In all panels, different line colors correspond to the inclusion ($N_{\rm max} = 1$) or not ($N_{\rm max} = 0$)
of the linear-in-spin QNM correction.
%
The joint posteriors are shown for illustrative purposes only. As we explain in Fig.~\ref{fig:edgb_cdf} and
in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}.
}
\label{fig:edgb_exec_sum}
\end{figure}

@@

In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
same way as already described for the EdGB and dCS theories.
%
We see that curves are very similar to those of dCS gravity for GW200129 (cf.
bottom panel in Fig.~\ref{fig:cEFT_cdf}).
%
Moreover, we find that the EFT~\eqref{eq:eft_bound} and
ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
$\mathfrak{m} = M_f$ and $N_{\rm max} = 1/2$.
%
This allows us to place the combined bound of
%
\begin{equation}
    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km}\,,
\end{equation}
%
at 90\% credibility. As also happened for our study for dCS, the find that for
the cubic EFT that the ParSpec bound is violated by the $n = 1$ corrections to
the QNMs, meaning that we cannot use this case to draw any meaningful
constraint on this parameter.
%
We summarize our results in Table~\ref{tab:summary_ceft}.

@@

In this theory, we considered only $N_{\rm max} = 0$. We found that the
inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
for which the ringdown portions of the larger than the inspiral-plunge part \dots
%
To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ simulations are breaking down other than
we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}

>>>>

\begin{figure}[t]
\includegraphics[width=\columnwidth]{figs/edgb_posteriors_combined.pdf}
\caption{(Color online).~Posterior distribution function on coupling constant $\ell_{\rm GB}$ in EdGB gravity
for GW150914 (top panel), GW200129 (middle panel)
and from combining results (bottom panel).
%
In all panels, different line colors correspond to the inclusion ($N_{\rm max} = 1$) or not ($N_{\rm max} = 0$)
of the linear-in-spin QNM correction.
%
The joint posteriors are shown for illustrative purposes only. As we explain in Fig.~\ref{fig:edgb_cdf} and
in the main text, our analysis of these events fails to satisfy the EFT bound~\eqref{eq:eft_bound}.
\agcomm{In all the figures of this kind, would it make sense to add grey vertical lines to
mark the 68\% and 90\% upper credible intervals? This will help the reader to quickly cross check the numbers
that are currently only mentioned in the text.}}
\label{fig:edgb_exec_sum}
\end{figure}

@@

In Fig.~\ref{fig:cEFT_cdf} we show the CDF for both events, calculated in the
same way as already described for the EdGB and dCS theories.
%
We see that curves are very similar to those of dCS gravity for GW200129 (cf.
bottom panel in Fig.~\ref{fig:cEFT_cdf}).
%
Moreover, we find that the EFT~\eqref{eq:eft_bound} and
ParSpec~\eqref{eq:parspec_bound} bounds are satisfied for both events both when
$\mathfrak{m} = M_f$ and $\epsilon = 1/2$.
%
This allows us to place the combined bound of
%
\begin{equation}
    \ell_{\rm cEFT} \leqslant 38.2~\textrm{km}\,,
\end{equation}
%
at 90\% credibility. As also happened for our study for dCS, the find that for
the cubic EFT that the ParSpec bound is violated by the $N_{\rm max} = 1$ corrections to
the QNMs, meaning that we cannot use this case to draw any meaningful
constraint on this parameter.
%
We summarize our results in Table~\ref{tab:summary_ceft}.

@@

In this theory, we considered only $N_{\rm max} = 0$. We found that the
inclusion of the spin corrections yields waveforms which for $\ell_{\rm qEFT} \gtrsim 80$~km
for which the ringdown portions of the larger than the inspiral-plunge part \dots
%
To avoid this issue we lowered the value of $\ell^{\rm max}_{\rm qEFT}$, but by doing so we obtained posteriors
which were essentially uniform. Thus, we do not quote any results for $N_{\rm max} = 1$.
%
Table~\ref{tab:summary_qeft} summarizes our findings for the quartic EFT of GR.
%
\hs{Discuss. I don't have a good argument for why the $N_{\rm max} = 1$ simulations are breaking down other than
we just fail to compute the waveform for $\ell_{\rm qEFT} = 80~$~km for GW150914-like masses.}
\agcomm{At the point of me going through this para, I am yet to figure out what's happening inside the code.
Hence I have not modified this text, but hopefully will have something over the coming days 
to sure up this point.}
